\section{Risks}\label{risks}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Risk name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Risk Description
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Risk Impact
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Solution
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Regulatory non-compliance (GDPR) & The system can expose sensible data
(name, ID, hire date) without respecting GDPR. & High, legal risk and
reputation risk & We can either accept this risk because our project
will not be public, or we can try to add compliant measures (hahsing) \\
Data Privacy & A user see sensible data, but he doesn't have the rights
to see these. & High, legal risk and reputation risk & We need to decide
which type of user can see what type of informations and then implement
these. Or accept this risk. \\
Incorrect data, not-updated, missing & Th represented data (shifts,
working hours, employees assigned to a working place, working place
details, etc\ldots) are not synchronized correctly because of a bug, a
failure, & High & ????? We accept it? \\
Insufficient log retention (for activity log UC-12) & Logs expire too
soon or are not archived & Low & Apply the right parameters (choose the
right time to keep activity logs) \\
Modification conflict & Two administrators modify the same data at the
same time.Overwriting of modifications, inconsistency between
assignments. & High & When developement, think of concurrent
modification to prevent this risk \\
No validation prior to major modification (add, remove, edit a user or a
working place) & No confirmation before modification or deletion.Risk of
irreversible human error. & High & Implement a validation system, a
message (``Are you sure you want to\ldots'') \\
Poor management of duplicates & Users, project, working places, etc..
are created multiple times & Medium & When developement, think of
managing duplicates to prevent this risk \\
Authentication service unavailable & Admin can no longer access their
account, critical operations blocked. & High, service interruption &
Accept this risk. \\
Unautorized access, security failure & A compromised admin account, or a
password leak that allow access to the system. & High, GDPR sanctions,
data breaches, manipulation of sensitive information & Use security
measures (multi-factor authentication, strong password, etc\ldots) \\
\end{longtable}
