\section{Epic: Timelink Admin
Platform}\label{epic-timelink-admin-platform}

\textbf{Epic ID:} EPIC-002 \textbf{Status:} \texttt{Proposed}
\textbf{Priority:} \texttt{High} \textbf{Theme:} Helping managers and
CEO's manage the working hours of their employees

\textbf{Created:} 15/10/2025 \textbf{Last Updated:} 16/10/2025
\textbf{Target Release:} 08/12/2025

% \begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{Epic Overview}\label{epic-overview}

\textbf{Business Problem:} Currently all managers do quite struggle to
manage and monitor the working hours of their workers and working places
respectively. It is really easy to make lose the amount of labor that
has been relaised in a working place or individual in live and in an
easy way.

\textbf{Business Value:} The Admin Platform helps companies save time
and reduce errors by showing all information in one clear system. It
makes it easier to see all the data represented in several graphical
representations.

\textbf{Success Metrics:} - Reduce manual work for administrators by at
least 60\% - 100\% synchronization between Admin Platform and Data
Server - Reach 95\% user satisfaction in the first release - System
uptime above 99.9\% during testing

% \begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{Scope}\label{scope}

\subsubsection{In Scope}\label{in-scope}

\begin{itemize}
\tightlist
\item
  Build a web-based Admin Platform using React Native
\item
  Connect the Admin Platform to the main Data Server (Spring Boot / SQL)
\item
  Create login and role-based access (admin users only)
\item
  Add dashboards with tables and graphs for all the employee data
\item
  Allow basic CRUD functions (create, read, update, delete) for all
  employee data
\end{itemize}

\subsubsection{Out of Scope}\label{out-of-scope}

\begin{itemize}
\tightlist
\item
  Full integration with external systems (like GPS tracking)
\item
  Data export in XML or other formats
\item
  Mobile version for admin users (web only for now)
\end{itemize}

% \begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{User Personas}\label{user-personas}

\begin{itemize}
\tightlist
\item
  \textbf{Admin User:} Works in HR or management. Needs to see and
  manage all employee data, hours, and working places quickly.
\item
  \textbf{Company Manager:} Supervises multiple workplaces and wants to
  be able to easily review statistics and reports.
\end{itemize}

% \begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{User Stories}\label{user-stories}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2381}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.3095}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2143}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2381}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Story ID
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Story Title
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Status
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Priority
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
US-5 & As an admin, I want to log in securely to the Admin Platform &
\texttt{Backlog} & \texttt{High} \\
US-6 & As an admin, I want to view employee working hours and working
places & \texttt{Backlog} & \texttt{High} \\
US-7 & As an admin, I want to see graphs of total hours worked per
working place & \texttt{Backlog} & \texttt{Medium} \\
US-8 & As an admin, I want to add and remove users from the system &
\texttt{Backlog} & \texttt{Medium} \\
US-9 & As an admin, I want to see connection status with the Data Server
& \texttt{Backlog} & \texttt{Low} \\
US-10 & As an admin, I want to filter employee data by department or
project, so that I can analyze work distribution more efficiently &
\texttt{Backlog} & \texttt{Medium} \\
US-11 & As an admin, I want to edit working places and assign employees
to them, so that I can maintain an up-to-date organizational structure &
\texttt{Backlog} & \texttt{High} \\
US-12 & As an admin, I want to view an activity log of recent changes in
the system, so that I can track who modified what and when &
\texttt{Backlog} & \texttt{Medium} \\
\end{longtable}

% \begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{Technical Considerations}\label{technical-considerations}

\textbf{Architecture Impact:} - The Admin Platform will communicate
directly with the Data Server using a REST Controller. - Requires a new
web frontend built with React Native for Web. - Backend data comes from
the existing Spring Boot server with SQL database.

\textbf{Dependencies:} - Data Server must be ready before Admin Platform
API integration.

\textbf{Risks \& Mitigations:} - \textbf{Risk 1:} Admin Platform may
load slowly with big data sets -- \emph{Mitigation:} Optimize queries. -
\textbf{Risk 2:} Inconsistent data between server and UI --
\emph{Mitigation:} Add sync checks and server-side validation.

\textbf{Non-Functional Requirements:}\\
- \textbf{Performance:} Pages should load in under 2 seconds. -
\textbf{Security:} Only authorized admin users can log in. -
\textbf{Scalability:} Should support up to 100 admin users per company.
- \textbf{Reliability:} 99.9\% uptime expected in testing phase.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

% \subsection{Definition of Ready}\label{definition-of-ready}

% \begin{itemize}
% \tightlist
% \item[$\boxtimes$]
%   Business value clearly defined
% \item[$\boxtimes$]
%   Success metrics established
% \item[$\boxtimes$]
%   High-level scope approved
% \item[$\boxtimes$]
%   User stories identified and estimated
% \item[$\square$]
%   Technical dependencies resolved
% \item[$\square$]
%   UX/design completed (not started yet)
% \end{itemize}

% \begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

% \subsection{Definition of Done}\label{definition-of-done}

% \begin{itemize}
% \tightlist
% \item[$\square$]
%   All user stories completed and accepted
% \item[$\square$]
%   Success metrics validated
% \item[$\square$]
%   Documentation updated
% \item[$\square$]
%   Integration tests passing
% \item[$\square$]
%   Performance requirements met
% \item[$\square$]
%   Deployed to production
% \item[$\square$]
%   Business stakeholders signed off
% \end{itemize}

% \begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

% \subsection{Open Questions}\label{open-questions}

% \begin{itemize}
% \tightlist
% \item
%   Is multi-language support required for version 1?
% \end{itemize}

% \begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

% \subsection{Related Artifacts}\label{related-artifacts}

% \begin{itemize}
% \tightlist
% \item
%   {[}Links to wireframes, technical designs, research, etc.{]}
% \end{itemize}
