\section{Use Case: Edit working places and assign employee to
them}\label{use-case-edit-working-places-and-assign-employee-to-them}

\textbf{Use Case ID:} UC-11\\
\textbf{Version:} 1.0\\
\textbf{Created:} 18/10/2025 \textbf{Last Updated:} 18/10/2025\\
\textbf{Priority:} \texttt{High}\\
\textbf{Status:} \texttt{Draft} \textbf{Related US:} US-11
\href{../US/US-11.md}{link}

\textbf{Primary Actor:} Admin\\
\textbf{Secondary Actors:} Data Server\\
\textbf{Stakeholders:}

\begin{itemize}
\tightlist
\item
  \textbf{Admin:} needs to keep employee assignments and working places
  up to date\\
\item
  \textbf{HR Department:} relies on accurate working place data for
  reports\\
\item
  \textbf{Company Management:} need updated employee locations for
  supervision and resource management
\end{itemize}

\textbf{Brief Description:}\\
This use case describes how an admin creates, edits, or deletes working
places and assigns or reassigns employees to those places. The goal is
to maintain an accurate and current organizational structure visible on
the dashboard and in reports.

\textbf{Trigger:}\\
The admin selects the ``Manage Working Places'' option from the
navigation menu.

\textbf{Preconditions:}

\begin{itemize}
\tightlist
\item
  Admin is authenticated and logged into the admin platform.\\
\item
  Data server is online and synchronized.\\
\item
  Admin has sufficient permissions to modify employee and working place
  data.
\end{itemize}

\textbf{Postconditions:} - Working place and employee assignment data
are updated successfully in the system. - Updated information is
reflected in dashboards and reports immediately.

\subsubsection{Main Success Scenario}\label{main-success-scenario}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.1579}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3947}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.4474}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Step
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Actor Action
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
System Response
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
1 & Admin navigates to the ``Working Places'' management page & System
displays the list of all current working places with assigned
employees \\
2 & Admin clicks ``Add New'' or selects a working place to edit & System
opens a form for adding, renaming, or deleting a working place \\
3 & Admin enters or modifies the working place details & System
validates the input \\
4 & Admin confirms changes & System saves the working place data and
updates the list \\
5 & Admin assigns or reassigns employees to a working place & System
updates employee records \\
6 & Admin saves assignments & Dashboard and reports reflect updated
structure in real-time \\
\end{longtable}

\subsubsection{Extensions (Alternative
Flows)}\label{extensions-alternative-flows}

\textbf{2a. Invalid or duplicate working place name}

\begin{itemize}
\tightlist
\item
  \textbf{Condition:} Admin enters invalid or duplicate working place
  name\\
\item
  \textbf{Action:} System displays an error message and prevents
  saving\\
\item
  \textbf{Result:} Admin should enter another name
\end{itemize}

\subsubsection{Special Requirements}\label{special-requirements}

\textbf{Performance:}\\
- Updates should be reflected on the dashboard within ? seconds.

\textbf{Security:}\\
- Only admin users with edit permissions can modify working place data.

\textbf{Technical Constraints:}\\
- Real-time update
