\section{Use Case: Filter employee data by department or
project}\label{use-case-filter-employee-data-by-department-or-project}

\textbf{Use Case ID:} UC-10\\
\textbf{Version:} 1.0\\
\textbf{Created:} 18/10/2025 \textbf{Last Updated:} 18/10/2025\\
\textbf{Priority:} \texttt{Medium}\\
\textbf{Status:} \texttt{Draft} \textbf{Related US:} US-10
\href{../US/US-10.md}{link}

\textbf{Primary Actor:} Admin\\
\textbf{Secondary Actors:} Data Server\\
\textbf{Stakeholders:}

\begin{itemize}
\tightlist
\item
  \textbf{Admin:} needs to quickly analyze employee distribution by
  department or project.\\
\item
  \textbf{HR Department:} uses filtered data for performance tracking
  and reporting.
\item
  \textbf{Company Managers:} need targeted insights for project
  management and ressources allocation.
\end{itemize}

\textbf{Brief Description:}\\
This use case describes how an admin filters employee data by department
or project in order to analyze work distribution. The system dynamically
updates the dashboard according to selected filtersand maitain these
filters across sessions until they are reset.

\textbf{Trigger:}\\
The admin selects one or more filters (department, project) on the admin
dashboard.

\textbf{Preconditions:}

\begin{itemize}
\tightlist
\item
  Admin is authenticated and logged into the admin platform.\\
\item
  Employee and project data are synchronized with the data server.\\
\item
  The dashboard is loaded and operational.
\end{itemize}

\textbf{Postconditions:}

\begin{itemize}
\tightlist
\item
  The system displays only employee data that match the selected
  filters.\\
\item
  The applied filters persist across sessions until manually reset.
\end{itemize}

\subsubsection{Main Success Scenario}\label{main-success-scenario}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.1579}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3947}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.4474}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Step
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Actor Action
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
System Response
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
1 & Admin navigates to the ``employee dashboard'' & System displays all
employee data by default \\
2 & Admin opens the filter panel & System displays the filter
options(department, project) \\
3 & Admin selects one or more filters & System queries filtered data
from the data server \\
4 & System retrieves the matching results & Dashboard updates
dynamically to display filtered employee data \\
5 & Admin closes the filter panel & System stores the selected
filters \\
\end{longtable}

\subsubsection{Extensions (Alternative
Flows)}\label{extensions-alternative-flows}

\textbf{2a.No matching data}

\begin{itemize}
\tightlist
\item
  \textbf{Condition:} there is no matching data for the given filters\\
\item
  \textbf{Action:} System displays a message (``There is no matching
  data for the filters: \ldots{}'')\\
\item
  \textbf{Result:} Admin may choose other filters
\end{itemize}

\subsubsection{Special Requirements}\label{special-requirements}

\textbf{Performance:}\\
- Filtered results must appear in under ? seconds.

\textbf{Usability:}\\
- Filters should be triggered and combinable intuitively.

\textbf{Persistence:}\\
- Filters must persist locally until reset.

\textbf{Scalability:}\\
- Filtering must handle up to ? departments and ? projects without
performance degradation.
