\subsection{Use Case: Employee
Reminder}\label{use-case-employee-reminder}

\textbf{Use Case ID:} UC-4\\
\textbf{Version:} 1.0\\
\textbf{Created:} 19/10/2025\\
\textbf{Last Updated:} 19/10/2025\\
\textbf{Priority:} \texttt{Low}\\
\textbf{Status:} \texttt{Draft}\\
\textbf{Related US:} US-4

\textbf{Primary Actor:} - Employee (Application User)

\textbf{Secondary Actors:} - Employer - Team Leader - Management

\textbf{Stakeholders:} - Company

\textbf{Brief Description:} This use case describes how the mobile app
automatically reminds an employee to start or end their shift if they
have forgotten to do so.\\
At scheduled times before or after the expected shift start and end
times, the system checks for missing punch-in our punch-out entries and
triggers a notification to prompt the user to take action.\\
This helps maintain accurate work-hour tracking and reduces
administrative corrections.

\textbf{Trigger:} User manually configures one or more reminder times in
the application settings.

\textbf{Preconditions:} - The user must be already logged into their
account in the application. - The application must have the appropriate
permissions to access system time. - Push notifications must be enabled
for the application. - There must be at least one shift available to
associate with the reminder.

\textbf{Postconditions:} - User receives a notification at the
configured times before or after the expected shift start or end times.
- User can open the application directly from the notification to start
or end the shift (Suggestion: If possible implement a ``Start Shift''
and ``End Shift'' option directly to the notification. This avoids user
even opening the application.).

\subsubsection{Main Success Scenario}\label{main-success-scenario}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.1622}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3784}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.4595}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Step
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Actor Action
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
System Response
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
1 & User configures a reminder for his shift (e.g., 5 min before shift
starts). & The application saves this reminder into its configuration
files. \\
2 & & The application sends a push notification at defined time (e.g.,
``Your shift starts in 5 minutes''). \\
3 & User opens the notification on their device. & The notification
provides direct action buttons (e.g., ``Start Shift'' or ``Open
App''). \\
4a & User taps the notification. & The application opens directly to
``Start Shift'' or ``End Shift'' button screen. \\
or & & \\
4b & User uses direct notification buttons to start or end shift. &
System updates shift status (records data) and notification
disappears \\
\end{longtable}

\subsubsection{Extensions (Alternative
Flows)}\label{extensions-alternative-flows}

\textbf{2a. Notifications Disabled by User}\\ - \textbf{Condition:} The
user has disabled notifications on their device (or specifically for
this application).\\ - \textbf{Action:} The application logs that
reminders cannot be sent.\\ - \textbf{Result:} No notification is
displayed.

\textbf{3a. Shift Already Started or Ended}\\
\emph{NOTE: In case reminders are set for after shift actions.}\\ -
\textbf{Condition:} The user already took the required action before the
reminder time.\\ - \textbf{Action:} The system cancels or suppresses the
reminder.\\ - \textbf{Result:} No notification sent.

\textbf{4a. Device Off or Do Not Disturb Mode On}\\ - \textbf{Condition:}
The user's device is off or in ``Do Not Disturb'' mode.\\ -
\textbf{Action:} The notification is queued and sent once conditions
allow.\\ - \textbf{Result:} Employee receives the notification later, with
correct timestamp.

\subsubsection{Special Requirements}\label{special-requirements}

\textbf{Performance:}\\ - Notifications must be delivered on time or at
the very least \textbf{within 30 seconds of expected time}.

\textbf{Security:}\\ - Notification must not display sensitive data (only
generic text such as ``Shift Start Reminder'').

\textbf{Reliability:}\\ - Reminder service should retry failed deliveries
up to 3 times.\\ - Missed notifications (notification not sent to user)
must be logged for later review.

\textbf{Technical Constraints:}\\ - Requires knowledge handling background
scheduling API (Android WorkManager or iOS BackgroundTasks)

\subsubsection{Open Issues}\label{open-issues}

\begin{itemize}
\tightlist
\item
  Should employer be able to create a reminder which cannot be turned
  off?
\item
  Should the application include recurring reminders (alert user that
  shift should have already started or ended)?
\end{itemize}
